---
title: "cleaning-script"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## cleaning script

### package loading

```{r}
library(tidyverse)
library(ggpubr)
```

### data loading and aggregation

* boston university

we begin by loading in the data associated with the first of the 11 listed sites, omitting rows one and three, which house additional variable-specifying information that will ultimately be captured in the metadata

```{r}
bu_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/boston-university.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) 
```

we will then need to remove the embedded separating column, `X`, and rename each of the variables according the conventions laid out in our codebook.

```{r}
bu_data <- bu_data %>%
  select(!X) %>%
  rename("date"=Site..BU,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1)
```

from this point, we will need to add an adjoining column specifying the site where these data correspond to

```{r}
bu_data <- bu_data %>% 
  mutate(site="boston university",
         .before="date")
```


now, we will perform the same series of changes to each of the remaining 10 sites

* culinary institute of america

```{r}
cia_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/culinary-institute-of-america.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..CIA,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="culinary institute of america",
         .before="date")
```

* rutgers university

```{r}
ru_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/rutgers-university.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..Rutgers,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="rutgers university",
         .before="date")
```


* san jose state university

```{r}
sjsu_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/san-jose-state-university.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..SJSU,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="san jose state university",
         .before="date")
```

* stanford university

```{r}
su_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/stanford-university.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..Stanford,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="stanford university",
         .before="date")
```

* university of bristol

```{r}
ub_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/university-of-bristol.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..Bristol,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="university of bristol",
         .before="date")
```


* university of california los angeles

```{r}
ucla_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/university-of-california-los-angeles.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..UCLA,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="university of california los angeles",
         .before="date")
```


* university of michigan

```{r}
um_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/university-of-michigan.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..University.of.Michigan,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="university of michigan",
         .before="date")
```

* university of north texas

```{r}
unt_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/university-of-north-texas.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..UNT,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="university of north texas",
         .before="date")
```


* university of reading

```{r}
ur_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/university-of-reading.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..University.of.Reading,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="university of reading",
         .before="date")
```


* vanderbilt university

```{r}
vu_data <- as_tibble(read.csv("/Users/kenjinchang/github/institutional-ingredient-repurposing/parent-data/csvs/vanderbilt-university.csv",skip=1)) %>%
  filter(!row_number() %in% c(1)) %>%
  select(!X) %>%
  rename("date"=Site..Vanderbilt,"prod_vol_purch"=Total.product.purchased,"prod_type"=Available.Product.Type..to.Prepare.for.Service.,"prod_vol_avail_upcyc"=Total.available.product.to.repurpose..after.primary.fabrication.or.preparation.,"prod_type_unavail_upcyc"=Product.Unable.to.Repurpose,"prod_vol_unavail_upcyc"=Total.available.product.left.that.cannot.be.repurposed..remaining.product.waste.,"meal_period"=Meal.Period.Utilization.Recipe.Served,"meal_swipes"=Meal.swipes.per.period,"recipe_served"=Recipe.Name,"prod_vol_in_recipe"=Volume.of.Repurposed.Ingredient.Used.in.Recipe,"recipe_cost"=Cost.per.recipe,"recipe_servings"=Servings.per.recipe,"displaced_recipe"=Displaced.Recipe.Name..Optional..if.replacing.something.on.the.line.,"displaced_recipe_vol"=Volume.that.would.have.been.served,"displaced_recipe_cost"=Cost.per.recipe.1,"displaced_recipe_servings"=Servings.per.recipe.1) %>%
  mutate(site="vanderbilt university",
         .before="date")
```


now that we have loaded in all of the data from the participating sites, we can begin the process of aggregating the individual site-level data


```{r}
aggregated_data <- bind_rows(bu_data,cia_data,ru_data,sjsu_data,su_data,ub_data,ucla_data,um_data,unt_data,ur_data,vu_data)
aggregated_data
```

## data cleaning

now that we've aggregated the data from the participating sites into one consolidated table, we'll need to modify the structure of the data and—in some cases—the inputted values, both to align the dataset with our analytical approach and to map site-provided responses (i.e., what respondents reported) with site-implemented practices (i.e., what sites did in practice)

in addition, there are some other reporting discrepancies that require standardization across sites (e.g., differences in the units reported for cost and weight)

we trace, detail, and justify each of these modifications below:

* format alignment

because there are subtle differences in how respondents' inputted their site-level information, there are some formatting refinements that need to be made in order accommodate some downstream functions

to identify these particularities, we consult the parent data in the `xlsxs` folder 

*san jose state university*
  
here, we see that the respondent appended unit identifiers within the columns containing weight values. this will ultimately introduce `NA` values by coercion in the subsequent step, where we convert columns containing numeric data from character strings to double-class vectors
  
to subvert this issue, which will invariably result in a loss of data, we will need to first remove these identifiers from the corresponding strings

```{r}
sjsu_data %>%
  mutate(prod_vol_purch=str_replace(prod_vol_purch,"lb","")) %>%
  mutate(prod_vol_purch=str_replace(prod_vol_purch,"oz",""))
###need to disaggregate mint and cilantro###
```

furthermore, we will also need to make a note here to convert the values that have been provided in ounces and gallons to pounds during the next cleaning stages 

because theseof each (need to separate mint and cilantro) - may need to create item-specific variable set first 

need to convert gallon to pounds (assume water)



* data structure changes

to address this initial concern, we will convert the columns containing numeric data from character strings (i.e., `<chr>`) to double strings (i.e., `<dbl>`)

more specifically, this includes the `prod_vol_purch`, `prod_vol_avail_upcyc`, `prod_vol_unavail_upcyc`, `meal_swipes`, `prod_vol_in_recipe`, `recipe_cost`, `recipe_servings`, `displaced_recipe_vol`, `displaced_recipe_cost`, `displaced_recipe_servings` variables.

```{r}
aggregated_data <- aggregated_data %>% 
  mutate(prod_vol_purch=as.numeric(prod_vol_purch)) %>%
  mutate(prod_vol_avail_upcyc=as.numeric(prod_vol_avail_upcyc)) %>%
  mutate(prod_vol_unavail_upcyc=as.numeric(prod_vol_unavail_upcyc)) %>%
  mutate(meal_swipes=as.numeric(meal_swipes)) %>%
  mutate(prod_vol_in_recipe=as.numeric(prod_vol_in_recipe)) %>%
  mutate(recipe_cost=as.numeric(recipe_cost)) %>%
  mutate(recipe_servings=as.numeric(recipe_servings)) %>%
  mutate(displaced_recipe_vol=as.numeric(displaced_recipe_vol)) %>%
  mutate(displaced_recipe_cost=as.numeric(displaced_recipe_cost)) %>%
  mutate(displaced_recipe_servings=as.numeric(displaced_recipe_servings)) 
```

* unit conversions

in addition, for the two participating sites in the UK (i.e., university of bristol and university of reading), we will need to perform conversions for the provided cost and weight values, transforming them from costs represented in pound sterlings to costs represented in USD and from weights represented in kilograms to weights represented in pounds

to accomplish this, we'll perform a conditional mutate that applies conversion factors of 2.205 (4sf) and 1.27 (3sf) to weight and cost values, respectively, that map onto those two institutions

more specifically, we will do this to each of the variables representing cost indices (i.e., `recipe_cost` and `displaced_recipe_cost`) and each of the variables representing weight indices (i.e., `prod_vol_purch`, `prod_vol_avail_upcyc`, `prod_vol_unavail_upcyc`, `prod_vol_in_recipe`, and `displaced_recipe_vol`)

```{r}
aggregated_data <- aggregated_data %>%
  mutate(case_when(site=="university of bristol" ~ recipe_cost==recipe_cost*1.27)) %>%
  mutate(case_when(site=="university of bristol" ~ displaced_recipe_cost==displaced_recipe_cost*1.27)) %>%
  mutate(case_when(site=="university of bristol" ~ prod_vol_purch==prod_vol_purch*2.205)) %>%
  mutate(case_when(site=="university of bristol" ~ prod_vol_avail_upcyc==prod_vol_avail_upcyc*2.205)) %>%
  mutate(case_when(site=="university of bristol" ~ prod_vol_unavail_upcyc==prod_vol_unavail_upcyc*2.205)) %>%
  mutate(case_when(site=="university of bristol" ~ prod_vol_in_recipe==prod_vol_in_recipe*2.205)) %>%
  mutate(case_when(site=="university of reading" ~ recipe_cost==recipe_cost*1.27)) %>%
  mutate(case_when(site=="university of reading" ~ displaced_recipe_cost==displaced_recipe_cost*1.27)) %>%
  mutate(case_when(site=="university of reading" ~ prod_vol_purch==prod_vol_purch*2.205)) %>%
  mutate(case_when(site=="university of reading" ~ prod_vol_avail_upcyc==prod_vol_avail_upcyc*2.205)) %>%
  mutate(case_when(site=="university of reading" ~ prod_vol_unavail_upcyc==prod_vol_unavail_upcyc*2.205)) %>%
  mutate(case_when(site=="university of reading" ~ prod_vol_in_recipe==prod_vol_in_recipe*2.205)) 
```

---- ^^^ still need to spot check whether this worked as intended ^^^ ---- 

* populating residual cells at day level

because the tibble contains data that correspond to different time intervals (i.e., some data that correspond to a single day and some data that correspond to a single meal period), we need to align the product-volume information such that they map onto each of the individual cells that correspond to the day the product was purchased and prepared

depending on the site, there are either three or four rows that correspond to the same date for each site, and the product-volume inputs—which are composed of the `prod_vol_purch`, `prod_type`, `prod_vol_avail_upcyc`, `prod_type_unavail_upcyc`, and `prod_vol_unavail_upcyc` variables—are frequently represented under just one of those three or four sets of cells for the individual day the specified ingredient was purchased and/or prepared

to correct this, we will need to consult the parent data tables located in the `xlsxs` folder within `parent-datasets` and make the corresponding adjustments in order to accommodate some of our downstream mutations

this will require us to first generate a new variable describing the number of ingredients that were purchased or prepared on a given day, and separate the `prod_vol_purch`, `prod_type`, `prod_vol_avail_upcyc`, `prod_type_unavail_upcyc`, and `prod_vol_unavail_upcyc` variables across the maximum number of ingredients purchased in a single day (by creating adjoining product-volume variables that are specific to each type of ingredient purchased or prepared)

```{r}
aggregated_data
```



******note to reflect this in codebook***** 

count_prod


this will require us to create a new variable-organization system that maps the previously identified `prod_vol_purch`, `prod_type`, `prod_vol_avail_upcyc`, `prod_type_unavail_upcyc`, and `prod_vol_unavail_upcyc` variables onto each day for all ingredients used. this should help with some downstream mutations, as it will allow us to retain a record of all the originally input volume-of-product information while also accommodating our time-interval data structure 

said differently, we will construct 

```{r}
aggregated_data
```

* inputting supplemental survey data 

* aligning date format

* mutating new variables 

### data writing and codebook documentation

```{r}
write.csv(aggregated_data,file="/Users/kenjinchang/github/institutional-ingredient-repurposing/data/aggregated-data.csv")
```


Variable ID | Variable Description
------------- | -------------
site  | The site at which the data was collected.
date  | The date during which the data was collected.
prod_vol_purch  | The total amount of the ingredient, or product, that was purchased by weight (in pounds). 
prod_type  | The type of ingredient, or product, that was available to be repurposed, or upcycled.
prod_vol_avail_upcyc  | The total amount of the ingredient, or product, that was available to be repurposed, or upcycled, by weight after primary fabrication (in pounds).
prod_type_unavail_upcyc  | The segments or portions of the available product that were not able to be repurposed, or upcycled.
prod_vol_unavail_upcyc  | The total amount of the ingredient, or product, that was unable to be repurposed, or upcycled, by weight (in pounds).
meal_period | The meal period, or interval, where the recipe was served
meal_swipes  | The number of entrance swipes that occurred during the corresponding meal period where the upcycled recipe was served (by count).
recipe_served  | The name of the recipe served.
prod_vol_in_recipe  | The total amount of the upcycled, or repurposed, ingredient used in the recipe by weight (in pounds).
recipe_cost  | The estimated cost of the served recipe (in USD).
recipe_servings  | The estimated number of servings yielded by the recipe.
displaced_recipe | The name of the recipe that would have otherwise been served had the repurposed recipe not been made.
displaced_recipe_vol | The total amount of recipe that would have otherwise been served by weight (in pounds).
displaced_recipe_cost | The estimated cost of the recipe that would have otherwise been served (in USD).
displaced_recipe_servings  | The estimated number of servings yielded by the recipe that would have otherwise been served.


